\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{banking} % Professional, header-centered style
\moderncvcolor{blue}                               

% Character encoding
\usepackage[utf8]{inputenc}

% Add color support for enhanced visual appeal
\usepackage{xcolor}

% Define custom colors - dark blue scheme
\definecolor{sectioncolor}{RGB}{0,30,60} % Dark blue for sections
\definecolor{highlightcolor}{RGB}{0,51,102} % Dark blue for highlights

% Adjust the page margins
\usepackage[scale=0.82, top=1.8cm, bottom=1.8cm]{geometry}

% Enhance section formatting with blue color
\renewcommand{\sectionfont}{\Large\mdseries\upshape\color{sectioncolor}}

% Personal Data
\name{Mahir Daiyan}{Safwaan}
\phone[mobile]{+8801880830398}
\email{msafwaan30@email.com} 
\social[linkedin]{safwaan30}

%----------------------------------------------------------------------------------
%            Content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle
\vspace{-2em}

\section{Professional Summary}
\cvitem{}{Technological Entrepreneur and Full-Stack Developer with over \textcolor{highlightcolor}{\textbf{1.5 years}} of experience in cross-platform mobile development (\textcolor{highlightcolor}{\textbf{React Native}}). Currently the \textcolor{highlightcolor}{\textbf{Founder \& CEO of ShadhinAI}}, dedicated to building inclusive democratic tools for marginalized communities. Deeply interested in \textcolor{highlightcolor}{\textbf{Avionics and GNC for Aerospace applications}}, combining high-level software engineering with low-level hardware integration.}

\section{Technical Skills}
\cvitem{Development}{\textcolor{highlightcolor}{\textbf{React Native, React.js, Node.js, Express, Firebase, Python}} (NumPy, SciPy, Matplotlib)}
\cvitem{Robotics \& Avionics}{\textcolor{highlightcolor}{\textbf{Avionics GNC, PID Control, Kalman Filters, STM32 Design, Altium Designer, KiCad}}}
\cvitem{Tools \& Automation}{\textcolor{highlightcolor}{\textbf{Selenium, WebScraping, BeautifulSoup, DiscordJS, Git, NASA's OPEN MCT, MQTT}}}
\cvitem{Programming Languages}{\textcolor{highlightcolor}{\textbf{JavaScript}} (Expert), \textbf{C/C++, Python, SQL}}

\section{Leadership \& Experience}

\cventry{2024--Present}{Founder \& CEO}{\textcolor{highlightcolor}{\textbf{ShadhinAI}}}{Dhaka, Bangladesh}{}{
\begin{itemize}
    \item \textbf{Visionary Leadership:} Conceptualized and launched an AI-driven platform focused on inclusive voting for senior citizens and persons with disabilities.
    \item \textbf{Full-Stack Engineering:} Architected and developed the entire mobile ecosystem from scratch using \textcolor{highlightcolor}{\textbf{React Native}}, ensuring accessibility (WCAG) compliance.
    \item \textbf{Capital Raising:} Successfully secured \textcolor{highlightcolor}{\textbf{2.5 Lakhs BDT in seed funding}} to accelerate product development and social outreach.
    \item \textbf{Strategic Growth:} Managing the product roadmap and engaging with democratic institutions to foster inclusive governance.
\end{itemize}}

\vspace{0.4em}

\cventry{Aug 2024--Present}{Avionics, GNC \& Propulsion Specialist}{\textcolor{highlightcolor}{\textbf{Amateur Experimental Rocketry Bangladesh (AERD)}}}{}{}{
\begin{itemize}
    \item Developed a proprietary \textcolor{highlightcolor}{\textbf{Ground Control System (GCS)}} for real-time telemetry and Cartesian-based servo control.
    \item Integrated \textcolor{highlightcolor}{\textbf{NASA's OPEN MCT}} for real-time visualization of high-frequency flight data.
    \item Engineered flight control software utilizing \textcolor{highlightcolor}{\textbf{Arduino and MQTT}} protocols for robust data transmission.
\end{itemize}}

\vspace{0.4em}

\cventry{Jan 2023--Dec 2023}{Vice-President}{\textcolor{highlightcolor}{\textbf{DRMC IT Club}}}{Dhaka, Bangladesh}{}{
\begin{itemize}
    \item \textbf{Event Management:} Organized the 5th DRMC International Tech Carnival, the largest tech event of its kind in Bangladesh, managing logistics and \textcolor{highlightcolor}{\textbf{100+ student volunteers}}.
    \item \textbf{Competition Hosting:} Spearheaded the first inter-college/university programming contest held at the Sheikh Rasel Digital Lab.
    \item \textbf{Sponsorship Acquisition:} Successfully negotiated and secured corporate sponsorships to fund large-scale club activities and carnivals.
\end{itemize}}

\vspace{0.4em}

\cventry{Apr 2024--Oct 2024}{Embedded Systems \& Avionics Intern}{\textcolor{highlightcolor}{\textbf{Dhumketu Exploration Company Limited}}}{}{}{
\begin{itemize}
    \item Designed a custom \textcolor{highlightcolor}{\textbf{2-layer STM32 PCB}} using Altium Designer, optimizing for size and signal integrity.
    \item Implemented \textcolor{highlightcolor}{\textbf{PID and Particle Filters}} to improve sensor accuracy in dynamic flight environments.
\end{itemize}}

\section{Education}
\cventry{Sep 2024--Present}{B.Sc. in Electrical and Electronics Engineering (EEE)}{\textcolor{highlightcolor}{\textbf{Rajshahi University of Engineering and Technology (RUET)}}}{Rajshahi}{}{\textit{Sophomore | Focusing on Control Systems and Embedded Architecture}}

\section{Honors \& Awards}
\begin{itemize}
    \item \textbf{Champion, Build4democracy Hackathon:} Recognized for developing ShadhinAI's accessible voting infrastructure to bridge the digital divide in democratic processes.
    \item \textbf{World Champion, 12th e-ICON World Contest:} Secured \textcolor{highlightcolor}{\textbf{1st place}} among \textcolor{highlightcolor}{\textbf{40+ competing nations}}, organized by the Ministry of Education, Republic of Korea.
    \item \textbf{National Finalist, NHSPC:} Represented Dhaka Residential Model College in the National High School Programming Contest (Standard Chartered Bank \& Prothom Alo).
\end{itemize}

\section{Featured Projects}
\begin{itemize}
    \item \textcolor{highlightcolor}{\textbf{ShadhinAI (React Native):}} A comprehensive, accessibility-first mobile application designed to enable independent voting for the visually impaired and elderly.
    \item \textcolor{highlightcolor}{\textbf{Until The EU (e-ICON Winner):}} A cross-platform mobile app that uses psychological tracking to mitigate student depression; awarded \textcolor{highlightcolor}{\textbf{1st prize globally}}.
    \item \textcolor{highlightcolor}{\textbf{bishleshok.ai:}} An AI-powered SME tool which came in \textcolor{highlightcolor}{\textbf{top 50}} in the Solvio Hackathon providing predictive analytics and business intelligence for local entrepreneurs.
\end{itemize}

\end{document}
